An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/trans.tex
starting on implementation
almost done

The translator takes as input a sample dataset of configuration files and transforms a given sample
dataset of configuration files into another set of files written in
typed and well-structured representations.
The translator can be seen a parser, and it is only
used to generate an intermediate representation for the post
process, such as learning rules (see $\S$\ref{sec-learn}).
Coupled with rules generated by learner module,
we will have a complete language model to verify configuration files
of our interest.

Translating or parsing is system dependent. In other words, for MySQL
and HDFS, we need to develop different parsers to handle each of them,
respectively. \app also allows users to 
provide extra help to the translator
for their specific system configurations,
but not necessarily. 
Each of the entries in the intermediate representations
have been assigned types, and these types guide the learning
modules later.

\para{Probabilistic types.}
For any key-value entry in the sample configuration files,
the translator cannot fully determine the type of key 
based on a single example value.
Consider the following example.

\begin{lstlisting}[language=C, xleftmargin=.01\textwidth]
foo = 300
bar = 300.txt
\end{lstlisting}

Most likely {\tt foo} should be an integer, but it could also be a string.
In this case, we want to learn the rule like 
$ \texttt{foo} \in \textsf{substrings}(\texttt{bar})$. 
The translator, therefore, assigns a distribution of types 
to a value, an idea closely related to existentially quantified 
types~\cite{Launchbury93lazyfunctional}. 
We introduce {\em probabilistic types} to address this issue.

Let $\mathcal{T}$ be a set of basic types. 
In \app set $\mathcal{T}$ contains strings, integers, file paths, 
sizes and IP addresses. 
A probabilistic type built from $\mathcal{T}$ is a list of pairs 
$[(\tau_1, p_1),\ldots,(\tau_n, p_n)]$,
such that $\tau_i \in \mathcal{T}$, $0 \le p_i \le 1$ 
and $\Sigma p_i = 1$. 
These probabilities are updated each time a new example value 
for a key is encountered.

@@

\para{Formal Intermediate Representation.}
The formal grammar we use for our intermediate representation presented in the following. 
Firstly, we make a list of the possible types for a configuration file. This is present in 
Secondly, we

\begin{table}
  \begin{tabular}{| l | c | r |}
    \hline
    Type & Operation & 3 \\ \hline
    4 & 5 & 6 \\ \hline
    7 & 8 & 9 \\
    \hline
  \end{tabular}
\caption{Table of Types Along with Operation Pools}
\label{table:kysymys}
\end{table}

>>>>

The translator takes as input a sample dataset of configuration files and transforms it into another set of files written in
typed and well-structured representations.
The translator can be seen a parser, and it is only
used to generate an intermediate representation for the post
process, such as learning rules (see $\S$\ref{sec-learn}).
Coupled with rules generated by learner module,
we will have a complete language model to verify configuration files
of our interest.

Translating or parsing is system dependent. In other words, for MySQL
and HDFS, we need to develop different parsers to handle each of them,
respectively. \app allows users to 
provide an extra help to the translator
for their specific system configurations,
but it is not required.

The majority of entries in a configuration files are assignments.Our first attempt was to simply
translate every key-value entry {\tt {k = v}} into a triple $(k, v, \tau)$, where $\tau$ is a type of 
$v$. However, sometimes we could not fully determine the type of key 
based on a single example value. For this reason, we introduced {\emph {probabilistic types}}.

Consider the following example.

\noindent{\tt {foo = 300}}\\
{\tt {bar = 300.txt}}

Most likely {\tt foo} should be an integer, but it could also be a string.
In the second case, we can learn the rule stating 
$ \texttt{foo} \in \textsf{substrings}(\texttt{bar})$. 
Instead of assigning one type to a value, the translator assigns a distribution of types 
to a value, an idea closely related to existentially quantified 
types~\cite{Launchbury93lazyfunctional}.

Formally, we define probabilistic types as follows: let $\mathcal{T}$ be a set of basic types (cf. Table~\ref{table:kysymys}).
A probabilistic type built from $\mathcal{T}$ is a list of pairs 
$[(\tau_1, p_1),\ldots,(\tau_n, p_n)]$,
such that $\tau_i \in \mathcal{T}$, $0 \le p_i \le 1$ 
and $\Sigma p_i = 1$. 
These probabilities are updated each time a new example value 
for a key is encountered.

@@

In \app set $\mathcal{T}$ contains strings, integers, file paths, 
sizes and IP addresses. With every type we associate a list of templates 
that are use to learn the rules about that files. Table~\ref{table:kysymys} contains
the most important types and templates.

\begin{table}
  \begin{tabular}{| l |  l |}
    \hline
    Type & Operation  \\ \hline
    Integer & $X = Y, X\neq Y, X \leq Y, X < Y, X * Y < Z, \ldots $\\ \hline
    String & $U = V, U \neq V, \textsf{prefix}(U,V), \textsf{sufix}(U,V), \ldots$   \\ \hline
    File & $\textsf{file}(F), \textsf{dir}(D),\ldots$   \\ \hline
    Size & similar as for integers   \\ \hline
    Port &    \\ \hline
    IP Addr.  &   \\

    \hline
  \end{tabular}
\caption{Table of types used in \app together with templates associated to every type}
\label{table:kysymys}
\end{table}

\para{Formal Intermediate Representation.}

An additional problem is that configuration files sometimes contain a simple version of the {\tt {if-then}} which 
sets under which conditions some actions should be applied.

The formal grammar we use for our intermediate representation presented in the following. 
Firstly, we make a list of the possible types for a configuration file. This is present in 
Secondly, we
